Future challenges for Research Software Engineering

### 2025-05-09 future_challenges_for_RSEng.tex
Fix some typos

\begin{story}{The greater world of Kim and Kay}{ethics}
10 years have passed since Kim and Kay have started on their journey of being RSEs. Back then,
at the universities of Eden and Utopia, life was more orderly and harmonious. Kay is working in a project that develops
software for cheap water monitoring devices in the global south. Kim is currently designing the software service stack
at her university, and increasingly struggles to find compelling Open Source alternatives that let's them keep their data
to software that is backed by large corporate entities. So far she still has the support of her university board, since it values
strategic autonomy.
Her son Kyle on the other hand started out with a degree in Physics and then took one of the newly created RSE Master courses,
but quickly decided that work in academia with its time limited contracts is not attractive.
Governments around the world are struggling to reposition themselves in this emerging deglobalized world with its new blocks
and therefore have deprioritized publicly funded research. Kyle decided to go to a defence company since they offer a
more secure employment in this polarized world.
\end{story}

\subsection{How have academic Institutions transformed by then?}
\begin{whatis}{What do we want to have achieved}{academic}
We hope to see that universities use the presence of an RSE Department actively as a means to differentiate themselves from other universities.
We hope that the central RSE units have local RSE representatives, or even small RSE groups that handle tasks within a department to oversee specific projects[FIXME: cite group paper].
We also hope, that specialized clusters form, with certain RSE units specializing in certain tasks like data management, HPC, or visualization.
At universities which have them, we want to see, that researchers naturally accept them as part of their used services.
\end{whatis}

@@

What are open questions here?
Organizations will have to come up with models for hiring people. While
a standardized RSE masters makes it easier, it will be interesting to see, if
RSE are still often hired by word of mouth or if the master's really makes it more comparable.

>>>>

\begin{story}{The greater world of Kim and Kay}{ethics}
10 years have passed since Kim and Kay have started on their journey of being RSEs. Back then,
at the universities of Eden and Utopia, life was more orderly and harmonious. Kay is working in a project that develops
software for cheap water monitoring devices in the global south. Kim is currently designing the software service stack
at her university, and increasingly struggles to find compelling Open Source alternatives that lets them keep their data
to software that is backed by large corporate entities. So far she still has the support of her university board, since it values
strategic autonomy.
Her son Kyle on the other hand started out with a degree in Physics and then took one of the newly created RSE Master's courses,
but quickly decided that work in academia with its time limited contracts is not attractive.
Governments around the world are struggling to reposition themselves in this emerging deglobalized world with its new blocks
and therefore have deprioritized publicly funded research. Kyle decided to go to a defense company since they offer a
more secure employment in this polarized world.
\end{story}

\subsection{How have academic Institutions transformed by then?}
\begin{whatis}{What do we want to have achieved}{academic}
We hope to see that universities use the presence of an RSE Department actively as a means to differentiate themselves from other universities.
We hope that the central RSE units have local RSE representatives, or even small RSE groups that handle tasks within a department to oversee specific projects[FIXME: cite group paper].
We also hope, that specialized clusters form, with certain RSE units specializing in certain tasks like data management, HPC, or visualization.
At universities which have them, we want to see that researchers naturally accept them as part of their used services.
\end{whatis}

@@

What are open questions here?
Organizations will have to come up with models for hiring people. While
a standardized RSE Master's makes it easier, it will be interesting to see if
RSE are still often hired by word of mouth or if the master's really makes it more comparable.
